\documentclass[10pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, urlcolor=Maroon]{hyperref}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{palatino}
\usepackage{longtable}
\renewcommand{\arraystretch}{0.75}
\setlength{\LTpre}{0pt}

\begin{document}

\begin{flushleft}
  {\Large \bfseries \sffamily Md Arif Shaikh}
  
  \vspace{0.25cm}
  
  {Postdoctoral Fellow\\
    \href{https://physics.snu.ac.kr/en}{Department of Physics and Astronomy}, \href{https://en.snu.ac.kr}{Seoul National University}\\
    1 Gwanak-ro, Gwanak-gu, Seoul 08826, Korea\\
    Email: \href{mailto:arif.shaikh@snu.ac.kr}{arif.shaikh@snu.ac.kr}, Web page: \href{https://md-arif-shaikh.github.io/}{md-arif-shaikh.github.io}\\
    \rule{\textwidth}{1pt}
  }
\end{flushleft}

{\itshape \noindent Postdoctoral researcher focusing on gravitation wave (GW) physics. My current research interests are modelling of eccentric waveforms using Numerical Relativity, GW physics with higher modes, test of general relativity with GW, gravitational lensing of GW. I am a current member of the \href{https://www.ligo.org/}{LIGO} Scientific Collaboration and the \href{https://www.black-holes.org/}{SXS} Collaboration.}

\section*{Positions}
\begin{tabular}{rp{14cm}}
  2022-- & {\sffamily {\bfseries Postdoctoral Fellow}},
               \href{https://physics.snu.ac.kr/en}{Department of Physics and Astronomy},
               \href{https://en.snu.ac.kr}{Seoul National University}\newline 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Korea\newline
               {\itshape Mentor}: Prof. \href{http://astro.snu.ac.kr/~hmlee/}{Hyung Mok Lee} $\cdot$ \href{mailto:hmlee@astro.snu.ac.kr}{hmlee@astro.snu.ac.kr}\\\\
  2019--2022 & {\sffamily {\bfseries Postdoctoral Fellow}},
              \href{https://www.icts.res.in/research/astrorel}{Astrophysical Relativity group}, \href{https://www.icts.res.in/}{International Centre for Theoretical Sciences}\newline
              Survey No. 151, Shivakote, Hesaraghatta Hobli, Bengaluru -- 560 089, India.\newline
              {\itshape Mentors}: Prof. P. Ajith $\cdot$ \href{mailto:ajith@icts.res.in}{ajith@icts.res.in}, Dr. P. Kumar $\cdot$ \href{mailto:prayush@icts.res.in}{prayush@icts.res.in}
\end{tabular}

\section*{Education}
\begin{tabular}{rp{14cm}}
  2014--2019 & {\sffamily \bfseries PhD}, \href{http://www.hri.res.in/}{Harish-Chandra Research Institute},
              Chhatnag Road, Jhunsi, Prayagraj (Allahabad), India\newline
              {\itshape Thesis Title:} On emergent sonic geometry through the linear perturbation of relativistic black hole accretion.\newline 
              {\itshape Thesis submitted}: June 25, 2019. {\itshape Thesis defended}: November 18, 2019\newline
              {\itshape Advisor}: Prof. Tapas K. Das $\cdot$ \href{mailto:tapas@hri.res.in}{tapas@hri.res.in}.\\ \\
  2012--2014 & {\sffamily \bfseries MSc}, \href{http://www.hri.res.in/}{Harish-Chandra Research Institute}, Chhatnag Road, Jhunsi, Prayagraj (Allahabad), India\newline
              {\itshape Percentage}: 77.05\%\newline\\
  2009--2012 & {\sffamily \bfseries BSc}, \href{http://www.jaduniv.edu.in/}{Jadavpur University}, Kolkata, India.\newline
              {\itshape Percentage}: 80.33\%
\end{tabular}

% \item {\bfseries Higher Secondary (10+2)}, Sarat Chandra Sur Institute, Kolkata, India. \hfill {\itshape 2007 -- 2009}\\
%  West Bengal Council of Higher Secondary Education.\\
%   {\itshape Percentage: 91.00\%}\\
%   Ranked {\bfseries \color{magenta} 16th} among about 0.4 million candidates.

% \item {\bfseries Secondary (10)}, Sihole High School, Dakshin Dinajpur, West Bengal, India. \hfill {\itshape 2007}\\
%   West Bengal Board of Secondary Education.\\
%   {\itshape Percentage: 99.37\%}\\
%   Ranked {\bfseries \color{magenta} 1st} among about 0.7 million candidates.


\section*{Publications}
\subsection*{Short-author publications}
\label{Short-author_publications}
\input{publication}
\subsection*{LIGO-VIRGO-KAGRA Collaboration publications}
\label{LIGO-VIRGO-KAGRA_Collaboration_publications}
\input{lvk_publication}


\section*{Conference, Workshops and Seminars}
\begin{longtable}{rp{14cm}}
  April 2022 & Poster on {\itshape Surrogate and hybrid models of eccentric waveforms using numerical relativity}, {\itshape 765. WE-Heraeus-Seminar: Gravitational Wave and Multimessenger Astronomy}, Bad Honnef, Germany, 25--28 April 2022.\\\\
  October 2021 & {\itshape LISC-Continuous Gravitational Waves Workshop (Virtual)}, 25-27 October, 2021.\\\\
  July 2021 & {\itshape Summer School on Gravitational-Wave Astronomy}, ICTS-TIFR, Bengaluru, 05-16 July, 2021. (Held online due to Covid19 outbreak).\\\\ 
  Feb 2021 & {Poster} on {\itshape Probing the evolution of compact binaries using higher modes of gravitational waves}, 39th ASI meeting, 18-23 Feb 2021, (Held online due to Covid19 outbreak).\\\\  
  Dec 2020 & {\itshape 31st meeting of the Indian Association for General Relativity and Gravitation (IAGRG)}, 19-20 Dec 2020, (IIT Gandhinagar. Held online due to Covid19 outbreak).\\\\

  Sep 2020 & {\itshape ICERM Fall '20 Workshop 1: Advances and Challenges in  
             Computational Relativity}, 14-18 September 2020, (held online due
             to Covid19 outbreak.)\\\\
  Sep 2020 & {Poster} on {\itshape Probing evolution history of compact
             binaries using higher modes of gravitational waves}, September 2020 LVK Meeting, 14-17 September 2020. (To be held online due to Covid19 outbreak.)\\\\

  Aug 2020 & {\itshape ICTS workshop on parameter estimation with bilby}, ICTS, Bengaluru, 27-28 August 2020. (To be held online due to covid19 outbreak)\\\\
  
  Aug 2020 & {\itshape Test of General Relativity using Gravitational Waves}, Indian Association for Cultivation of Science, Kolkata and Indian Institute of Technology, Gandhinagar, 13--14 August 2020. (Held online due to Covid19 outbreak).\\\\
  
  Jun 2020 & {\itshape PyCBC Inference Online Workshop 2020}, Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Germany. 25--26 June 2020, (Held online due to Covid19 outbreak)\\\\
  
  May 2020 & {\itshape Gravitational-Wave Open Data Workshop \#3}, LIGO-Virgo Collaboration, 26-28 May, 2020. (Held online due to Covid19 outbreak).\\\\
  
  May 2020 & {\itshape Summer School on Gravitational-Wave Astronomy}, ICTS-TIFR, Bengaluru, 18-23 May, 2020. (Held online due to Covid19 outbreak).\\\\
  
Feb 2020 & {Talk} on {\itshape Probing the evolution history of compact binaries from higher modes of gravitation waves}, ICTS In-house symposium, ICTS-TIFR, Bengaluru, 17--18 February 2020.\\\\ %\href{https://www.youtube.com/watch?v=UhRhe5N2wFY&list=PL04QVxpjcnjjPNIjfxpc0BYxvSMsd57Ko&index=29&t=0s}{Link}.

 Dec 2019 & {\itshape Astrophysics of Supermassive Black Holes}, ICTS, Bengaluru, 17--19 December, 2019.\\\\

 Dec 2019 & {\itshape Newton Bhabha-Open Data workshop}, IUCAA, Pune, 4--6 December, 2019.\\\\
  
 Nov 2019 & {Talk} on {\itshape On the emergent sonic geometry through the linear perturbation of relativistic black hole accretion}, Harish-Chandra Research Institute, Prayagraj, 18 November 2019.\\\\

Aug 2019 & {\itshape The Future of Gravitational-Wave Astronomy}, ICTS, Bengaluru, 19--22 August 2019.\\\\

Jul 2019 & {\itshape Summer School on Gravitational-Wave Astronomy}, ICTS, Bengaluru, 15--26 July 2019.\\\\

Mar 2019 & {\itshape Theoretical Aspects of Astroparticle Physics, Cosmology and Gravitation}, the Galileo Galilei Institute for Theoretical Physics, Florence, Italy, 11--22 March 2019\\\\
  
Nov 2018 & {Talk} on {\itshape Relativistic acoustic geometry in general relativistic accretion disc around Kerr black holes}, Exploring the Universe: Near Earth Space Science to Extra-Galactic Astronomy, S N Bose National Centre for Basic Sciences, Kolkata, 14--17 November 2018.\\\\

Dec 2017 & {\itshape Black Holes: From Classical to Quantum Gravity}, IIT Gandhinagar, 15--19 December 2017.\\\\

Sep 2017 & {Talk} on {\itshape Emergence of curved sonic manifold for isothermal accretion in black hole metric}, Young Astronomers Meet, IUCAA, Pune, 11--15 September 2017\\\\

Jul 2017 & {\itshape Summer School on Gravitational-Wave Astronomy}, ICTS, Bengaluru, 17--28 July 2017.\\\\

May 2017 & {Poster} on {\itshape Relativistic sonic geometry for isothermal accretion in Kerr metric}, 29th meeting of Indian Association of General Relativity and Gravitation (IAGRG), IIT Guwahati, 18--20 May 2017\\\\

Mar 2017 & {Poster} on {\itshape Emergence of relativistic sonic geometry through perturbation of matter in black hole metric}, 35th meeting of Astronomical Society of India (ASI), Jaipur, 6--10 March 2017.
% \item {\itshape Workshop on Black Hole Information Paradox}, HRI, Allahabad, 3--6 February 2014.
\end{longtable}


\section*{Awards, Fellowships and others}
\begin{longtable}{rp{14cm}}
Feb 2021 & Membership of \href{https://www.black-holes.org/}{SXS} Collaboration.\\\\
Aug 2020 & Membership of \href{https://www.ligo.org/}{LIGO} Scientific Collaboration.\\\\
2018 & HRI--Infosys Prize for the year 2018 for distinction in research in Astrophysics.\\\\
Dec 2017 & West Bengal State Eligibility Test (WBSET).\\\\
Jun 2017 & National Eligibility Test for JRF (NET).\\\\
Dec 2016 & National Eligibility Test for JRF (NET).\\\\
Feb 2017 & Graduate Aptitude Test (GATE).\\\\
2012--2014 & Senior Research Fellowship, DAE, Govt. of India.\\\\
2014--2018 & Junior Research Fellowship, DAE, Govt. of India.\\\\
Jul 2012 & Offer for PhD at \href{https://www.iucaa.in/}{IUCAA}, Pune starting in 2014 (declined).\\\\
Jul 2012 & Offer for Integrated PhD at \href{http://www.ncra.tifr.res.in/ncra/main}{NCRA-TIFR}, Pune (declined).\\\\
Jun 2012 & Offer for Integrated PhD at \href{https://www.iisc.ac.in/}{IISc}, Bangalore (declined).\\\\
May 2012 & Offer for M.Sc at \href{http://www.iitb.ac.in/}{IIT Bombay} (declined).\\\\
Feb 2012 & Joint Entrance Screening Test (JEST).\\\\
Feb 2012 & Joint Admission Test for M.Sc (JAM).\\\\
2009--2012 & INSPIRE Fellowship, DST, Govt. of India.\\\\
2009 & {16th} rank in 10+2 standard examination, West Bengal Board of Secondary Education.\\\\
2007 & {1st} rank in 10 standard examination, West Bengal Council of Higher Secondary Education.
\end{longtable}



\section*{Refereeing}
\begin{itemize}
\item \href{https://iopscience.iop.org/journal/0264-9381}{Classical and Quantum Gravity}
\item \href{https://epjc.epj.org/}{The European Physical Journal C}
\end{itemize}


\section*{Teaching Assistantship}
\begin{longtable}{rp{14cm}}
  October 2021 & Tutored in the workshop {\itshape LISC - Continuous Gravitational Waves Workshop (Virtual)}, 25-27 October 2021.\\\\
  July 2021 & {Tutored} a course on ``{\bfseries Stochastic gravitational wave background from early universe}'' at the {\itshape Summer School on Gravitational Wave Astronomy}, July 2021 at ICTS-TIFR, Bengaluru. This course was instructed by Prof. Shi Pi of Kavli Institute for Physics and Mathematics of the Universe, Japan.\\\\
  Aug--Dec 2020 & {Tutored} a semester course on ``{\bfseries Introduction to General Relativity}", Aug-Dec 2020, ICTS-TIFR, Bengaluru. This course was instructed by Prof. Bala Iyer.\\\\
  
  Aug 2020 & {Tutored} in {\itshape ICTS workshop on parameter estimation with bilby}, ICTS, Bengaluru, 27-28 August 2020. Workshop repository is \href{https://github.com/GregoryAshton/GWParameterEstimationWorkshop2020}{here}.\\\\
  
  May--Jun 2020 & {Tutored} a course on {\bfseries ``Numerical Hydrodynamics''} at the {\itshape Summer School on Gravitational Wave Astronomy}, May--June 2020 at ICTS-TIFR, Bengaluru. This course was instructed by Prof. Ian Hawke of University of Southampton.\\\\
  
  May 2020 & {Mentored} Mr. Uddeepta Deka, a graduate student at ICTS-TIFR, for his term paper on {\bfseries ``Formation channels of BBHs detected in LIGO''}, May, 2020.\\\\
  
  Jan--Apr 2020 & {Tutored} a semester course on {\bfseries ``An Introduction to GW Physics \& Astronomy''}, Jan--Apr 2020 at ICTS-TIFR, Bengaluru. This course was instructed by Prof P. Ajith and Prof Bala Iyer.\\\\

  15--26 Jul 2019 & {Tutored} a course on {\bfseries ``Advanced General Relativity''} at the {\itshape Summer School on Gravitational Wave Astronomy}, 15--26 July 2019 at ICTS-TIFR, Bengaluru. This course was instructed by Prof. Sudipta Sarkar of IIT, Gandhinagar, India.\\\\

  Jan--May 2016 & {Tutored} a semister course on {\bfseries ``Statistical Physics''} at Harish-Chandra Research Institute, Allahabad, Jan--May 2016. The course was instructed by Prof G. V. Pai.\\\\

  May--Jun 2015 & {Mentored} Mr Soumyadeep Chatterjee, a postgraduate student from IIT Bombay, who was visiting the Cosmology and High Energy Astrophysics group at HRI during May--June 2015. He studied accretion flow in binary star system via Roche lobe overflow.
\end{longtable}


\section*{Visits}
\begin{longtable}{rp{14cm}}
Apr 2022 & Frank Ohme, Albert Einstein Institute, Max Planck Institute for Gravitational Physics, Hannover, Germany, April 20--April 24, 2022.\\\\
Mar--Apr 2022 & Harald Pfeiffer, Albert Einstein Institute, Max Planck Institute for Gravitational Physics, Potsdam, Germany, March 20 -- April 20, 2022.\\\\
Nov 2019 & Tapas K. Das, Harish-Chandra Research Institute, Nov 15--25, 2019.\\\\
Mar--Apr 2019 & P. Ajith, ICTS-TIFR, Bengaluru, March 25--April 6, 2019.\\\\
Jun 2018 & Subir Gosh, Indian Statistical Institute, Kolkata, 11--22 June 2018.\\\\
Feb--Mar 2018 & Sankhasubhra Nag, Sarojini Naidu College for Women, Kolkata, 14 February--4 March 2018.\\\\
Nov--Dec 2017 & S. N. Bose National Centre for Basic Sciences, Kolkata, 18 November--1 December 2017.\\\\
Sep--Oct 2017 & P. Ajith, ICTS-TIFR, Bengaluru, 27 September--11 October 2017.\\\\
Nov 2016 & Sagar Chakraborty, IIT Kanpur, 22--23 November 2016.\\\\
Sep--Oct 2014 & Tarun Souradeep, IUCAA Pune, 6 September--20 October 2014.
\end{longtable}

\section*{Computational Skills}
\begin{longtable}{rp{14cm}}
{\bfseries Programming languages} & Python, Julia, C++, Emacs Lisp, Racket\\\\
{\bfseries Scientific software} & SpEC, Bilby, PyCBC, Matplotlib, Mathematica, \LaTeX, Emacs, Gnuplot\\\\
{\bfseries Operating systems} & Linux, MacOS, Windows.
\end{longtable}


\section*{References}
\begin{itemize}
\item Prof. \href{http://www.hri.res.in/people/Physics/tapas}{Tapas Kumar Das} ({\bfseries PhD advisor})\\
  Associate Proffesor G\\
  Harish-Chandra Research Institute\\
  Chhatnag Road, Jhunsi, Allahabad 211019, India.\\
  Email: {tapas@hri.res.in}\\
  %Mobile No.: +91 98300 91113\\
  Phone No. (office): +91 5322274321
  
\item Prof. \href{https://home.icts.res.in/~ajith/Home.html}{Parameswaran Ajith} ({\bfseries Postdoc mentor})\\
  Associate Professor\\
  International Centre for Theoretical Sciences, Bengaluru, India\\
  Email: {ajith@icts.res.in}\\
  Phone No. (office): +91 80 4653 6210

\item Prof. \href{https://www.icts.res.in/people/prayush-kumar-0}{Prayush Kumar} ({\bfseries Postdoc mentor})\\
  Reader\\
  International Centre for Theoretical Sciences, Bengaluru, India\\
  Email: {prayush@icts.res.in}\\
  Phone No. (office): +91 80 4653 6390

\item Dr. {Shasvath Kapadia}\\
  Assistant Professor\\
  \href{https://www.iucaa.in/}{The Inter-University Centre for Astronomy and Astrophysics, Pune, India}\\
  Email: {shasvath.kapadia@iucaa.in}
  
\item Dr. \href{https://vijayvarma.com/}{Vijay Varma}\\
  Marie Curie Fellow\\
  Albert Einstein Institute, Potsdam, Germany\\
  Email: vijay.varma@aei.mpg.de, vijay.varma392@gmail.com

% \item Prof. \href{https://www.icts.res.in/people/bala-iyer}{Bala Iyer}\\
%   Simons Visiting Professor\\
%   International Centre for Theoretical Sciences, Bengaluru, India\\
%   Email: {bala.iyer@icts.res.in}\\
%   Phone No. (office): +91 80 4653 6360
\end{itemize}


\section*{Personal Information}
\begin{longtable}{rp{14cm}}
{\bfseries Date of birth} & April 18, 1992\\\\
{\bfseries Nationality} & Indian\\\\
{\bfseries Languages} & Bengali, English, Hindi.\\\\
{\bfseries Marital status} & Married.
\end{longtable}

\end{document}