\begin{enumerate}
\item Maity, S., \underline{Shaikh, M. A.}, Tarafdar, P. \& Das, T. K., {\itshape {Carter-Penrose diagrams for emergent spacetime in axisymmetrically accreting black hole systems}}, \href{https://journals.aps.org/prd/accepted/6a071Q0dF6310e3391c4857600be1cb84620086cd?fbclid=IwAR3b3H83dOHQq9BihVVwKJMehm5EX3b2mSBVduUXGBPgL8dWPUR7LDcVCnI}{{Phys. Rev. D}}, {\bfseries Accepted} (2022).
\item Singh, M. K., Kapadia, S. J., Divyajyoti, \underline{Shaikh, M. A.} \& Ajith, P., {\itshape {Improved early-warning estimates of luminosity distance and orbital inclination of compact binary mergers}}, \href{https://doi.org/10.1093/mnras/stac852}{{Monthly Notices of the Royal Astronomical Society}}, {\bfseries 513}, 3798–3809, (2022).
\item Wei, W., Huerta, E. A., Yun, M., Loutrel, N.,  \underline{Shaikh, M. A.}, Kumar, P., Hass, R. \& Kindratenko, V., {\itshape  Deep Learning with Quantized Neural Networks for Gravitational Wave Forecasting of Eccentric Compact Binary Coalescence}, \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac1121}{The Astrophysical Journal}, {\bfseries 919}, 82, (2021).
\item Singh, M. K., Kapadia, S. J., \underline{Shaikh, M. A.}, Chatterjee, D. \& Ajith, P., {\itshape {Improved early warning of compact binary mergers using higher modes of gravitational radiation: a population study}}, \href{https://doi.org/10.1093/mnras/stab125}{{Monthly Notices of the Royal Astronomical Society}}, {\bfseries 502}, 1612-1622, (2021).
\item Kapadia, S. J., Singh, M. K., \underline{Shaikh, M. A.}, Chatterjee, D. \& Ajith, P., {\itshape Of Harbingers and Higher Modes: Improved Gravitational-wave Early Warning of Compact Binary Mergers}, \href{https://doi.org/10.3847%2F2041-8213%2Faba42d}{{The Astrophysical Journal Letters}}, {\bfseries 898}, L39, (2020).
\item \underline{Shaikh, M. A.} \& Das, T. K., {\itshape Linear perturbations of low angular momentum accretion flow in the Kerr metric and the corresponding emergent gravity phenomena}, \href{https://link.aps.org/doi/10.1103/PhysRevD.98.123022}{{Phys. Rev. D}}, {\bfseries 98}, 123022, (2018).
\item \underline{Shaikh, M. A.}, Maity, S., Nag, S. \& Das, T. K., {\itshape Effective sound speed in relativistic accretion discs around Schwarzschild black holes}, \href{http://www.sciencedirect.com/science/article/pii/S1384107618302896}{{New Astronomy}}, {\bfseries 69}, 48 - 57, (2019).
\item Datta, S., \underline{Shaikh, M. A.} \& Das, T. K., {\itshape Acoustic geometry obtained through the perturbation of the Bernoulli's constant}, \href{http://www.sciencedirect.com/science/article/pii/S1384107617301847}{{New Astronomy}}, {\bfseries 63}, 65 - 74, (2018).
\item \underline{Shaikh, M. A.}, {\itshape Relativistic sonic geometry for isothermal accretion in the Kerr metric}, \href{https://doi.org/10.1088%2F1361-6382%2Faaa5cd}{{Classical and Quantum Gravity}}, {\bfseries 35}, 055002, (2018).
\item \underline{Shaikh, M. A.}, Firdousi, I. \& Das, T. K., {\itshape Relativistic sonic geometry for isothermal accretion in the Schwarzschild metric}, \href{https://doi.org/10.1088%2F1361-6382%2Faa7b19}{{Classical and Quantum Gravity}}, {\bfseries 34}, 155008, (2017).
\end{enumerate}
